---
title: "FakeDiamond: find concreteness word pairs"
author: "Ryan Law"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(LexOPS)
library(tidyverse)
```

## Generate a list of single words 

We generate a list of concrete and abstract words by sampling from the two local maxima in the concrete rating distribution, ranging from 1 to 7, from the Glasgow Norms (Scott et al., 2018). Concrete words were drawn from the range of 2.5-3.5, while abstract words were drawn from the distribution between the range of 6-7. 

All pairs of concrete-abstract words are matched on several psycholinguistic variables known to influence lexical and conceptual access: 
- single word frequency in Zipf (frequency per billion words; variance +-0.1)
- word length (variance +-2 characters)
- age of acquisition (variance +-0.1)
- part-of-speech 
The list is further filtered based on the proportion of people knowing that word at 0.9-1. That is, we keep only words that 90% of raters know. 


```{r create list of words}
stim <- LexOPS::lexops %>%
	subset(PK.Brysbaert >= 0.9 & PK.Brysbaert <= 1) %>%
	split_by(CNC.Brysbaert, 1.5:2.5 ~ 4:5) %>%
	control_for(Zipf.SUBTLEX_UK, -0.3:0.3) %>%
	control_for(AoA.Kuperman, -2:2) %>%
	control_for(PoS.SUBTLEX_UK) %>%
	control_for(Length, -2:2) %>%
	generate("all", "balanced", seed = 42)
stim_long <- long_format(stim)
rep_str = c('A1'='Abstract','A2'='Concrete')
stim_long$condition <- str_replace_all(stim_long$condition, rep_str)
write.csv(stim_long, "U:\\ownCloud\\projects\\semantic_composition\\stimuli\\stim_long_brysbaert_all_possible_seed42.csv", row.names=FALSE)
stim_long
```

## Examine distribution

```{r visualise design, echo=FALSE}
plot_design(stim_long)
```

## Examine SD of concreteness to make sure raters agree with ratings

```{r visualise SD, echo=FALSE}

```
